New seismological constraints on the available parameter space of macroscopic dark matter

### 2016-09-11 LaTeX/Article_Draft_EDITED.tex
Update

The seismometers on the moon have a net useful range of up to $16\,\te{Hz}$ and are sensitive to displacements as small as $0.3\,\text{nm}$ \cite{latham1973lunar}\cite{nakamura1982apollo}. Therefore, we only calculate the energy contained in the modes of frequency less than $16\,\te{Hz}$.

>>>>

The seismometers on the moon have a net useful range of up to $20\,\te{Hz}$ and are sensitive to displacements as small as $0.3\,\text{nm}$ \cite{latham1973lunar}\cite{nakamura1982apollo}. Therefore, we only calculate the energy contained in the modes of frequency less than $20\,\te{Hz}$.
